Estimating nucleon substructure properties in a\\[.2ex] unified hydrodynamic model of p-Pb and Pb-Pb collisions

### 2018-05-07 talk/qm2018.tex
Add some validation material to talk slides

\begin{frame}[plain]
  \begin{tikzpicture}
    \node {\includegraphics[height=.98\paperheight]{posterior}};
    \node (title) at (6.0, 3.5) {\color{theme}{\scshape \Large Bayesian posterior}};
    \node<1>[draw=none, text width=6.5cm, align=left, below=.4cm of title] (b1) {%
      \small One row (column) for each parameter
      };
    \node<1>[draw=none, text width=6.5cm, align=left, below=.1cm of b1] (b2) {%
      \small Diagonal panels: marginal distribution of a single model parameter
      };
    \node<1>[draw=none, text width=6.5cm, align=left, below=.1cm of b2] (b3) {%
      \small Off-diagonal panels: joint distribution between a pair of model parameters
      };
    \node<1>[draw=none, text width=6.5cm, align=left, below=.2cm of b3] (b4) {%
      \textcolor{theme}{Let's look at some specific regions...}
      };
    \draw<1>[->, thick, theme] (b2.west) to [out=180, in=90] (-.35, .8);
    \draw<1>[->, thick, theme] (b3.west) to [out=180, in=90] (.1, -.95);
    \node<2>[xshift=-2.7cm, yshift=3.2cm, scale=.3] {\includegraphics[scale=.15]{magnifying-glass}};
    \node<2>[below=.4cm of title, align=center] {
        \includegraphics[scale=.8]{posterior_p}\\[2ex]
        \small Initial entropy deposition\\
        \small consistent with geometric mean\\[.5ex]
        $dS/dy \sim \sqrt{T_A T_B}$
      };
    \node<3>[xshift=-1.05cm, yshift=1.5cm, scale=.3] {\includegraphics[scale=.15]{magnifying-glass}};
    \node<3>[below=.4cm of title, align=center] {
        \includegraphics[scale=.8]{posterior_parton_number}\\[2ex]
        \small Evidence for nucleon substructure $N_\text{partons} > 1$.\\
        \small Does not prefer a specific parton number.
      };
    \node<4>[xshift=.62cm, yshift=-.15cm, scale=.3] {\includegraphics[scale=.15]{magnifying-glass}};
    \node<4>[below=.4cm of title, align=center] {
        \includegraphics[scale=.8]{posterior_freestreaming}\\[2ex]
        \small Analysis cannot tolerate free-streaming\\
        \small times larger than ${\sim} 1$~fm/$c$
      };
    \node<5>[xshift=-.5cm, yshift=.9cm, scale=.3] {\includegraphics[scale=.15]{magnifying-glass}};
    \node<5>[below=.4cm of title, align=center] {
        \includegraphics[scale=.8]{posterior_structure}\\[2ex]
        \small Parton structure parameter $\chi_\mathrm{struct} = 0.28_{-0.16}^{+0.17}$,\\
        \small Was used to reparametrize parton width as\\[.5ex]
        \small $v = v_\text{min} + \chi_\text{struct}(w - v_\text{min})$.\\[1ex]
        \small \hfill Let's revert $\chi_\text{struct}$ back to a width...
      };
  \end{tikzpicture}
\end{frame}

\begin{frame}{\scshape Nucleon size and shape}
  \begin{columns}
    \begin{column}{.45\textwidth}
      \begin{figure}
        \includegraphics[width=\textwidth]{proton_posterior_shape}
      \end{figure}
    \end{column}
    \begin{column}{.55\textwidth}
      \begin{itemize}
        \item Nucleon width\, $w = 0.9_{-0.14}^{+0.16}$~fm\\[.5ex]
          (consistent with rms charge radius)\\[2ex]
        \item Parton width\, $v = 0.4_{-0.14}^{+0.16}$~fm\\[2ex]
        \item Results likely sensitive to model details,
          e.g.\ equation of state, pre-equilibirum dynamics and viscous
          corrections $\delta f$\\[2ex]
        \item Nevertheless tantalizing question, can hydro be used
          to measure the size and shape of the proton?
      \end{itemize}
    \end{column}
  \end{columns}
\end{frame}

\begin{frame}{\scshape QGP viscosities}
  \bigskip
  \begin{columns}
    \begin{column}{.6\textwidth}
      \includegraphics[width=\textwidth]{fig/region_shear_bulk_blank}\\[2ex]
      \includegraphics[width=\textwidth]{fig/region_shear_bulk}
    \end{column}
    \begin{column}{.4\textwidth}
      p-Pb \& Pb-Pb at 5.02 TeV
    \end{column}
  \end{columns}
\end{frame}

>>>>

\begin{frame}[plain]
  \begin{tikzpicture}
    \node {\includegraphics[height=.98\paperheight]{posterior}};
    \node (title) at (5.75, 3.5) {\color{theme}{\scshape \Large Bayesian posterior}};
    \node<1>[draw=none, text width=6.5cm, align=left, below=.4cm of title] (b1) {%
      \small One row (column) for each parameter
      };
    \node<1>[draw=none, text width=6.5cm, align=left, below=.1cm of b1] (b2) {%
      \small Diagonal panels: marginal distribution of a single model parameter
      };
    \node<1>[draw=none, text width=6.5cm, align=left, below=.1cm of b2] (b3) {%
      \small Off-diagonal panels: joint distribution between a pair of model parameters
      };
    \node<1>[draw=none, text width=6.5cm, align=left, below=.2cm of b3] (b4) {%
      \textcolor{theme}{Let's look at some specific regions...}
      };
    \draw<1>[->, thick, theme] (b2.west) to [out=180, in=90] (-.35, .8);
    \draw<1>[->, thick, theme] (b3.west) to [out=180, in=90] (.1, -.95);
    \node<2>[xshift=-2.7cm, yshift=3.2cm, scale=.3] {\includegraphics[scale=.15]{magnifying-glass}};
    \node<2>[below=.4cm of title, align=center] {
        \includegraphics[scale=.7]{posterior_p}\\[2ex]
        \small Initial entropy deposition\\
        \small consistent with geometric mean\\[.5ex]
        $dS/dy \sim \sqrt{T_A T_B}$
      };
    \node<3>[xshift=-1.05cm, yshift=1.5cm, scale=.3] {\includegraphics[scale=.15]{magnifying-glass}};
    \node<3>[below=.4cm of title, align=center] {
        \includegraphics[scale=.7]{posterior_parton_number}\\[2ex]
        \small Evidence for nucleon substructure $N_\text{partons} > 1$.\\
        \small Does not prefer a specific parton number.
      };
    \node<4>[xshift=.62cm, yshift=-.15cm, scale=.3] {\includegraphics[scale=.15]{magnifying-glass}};
    \node<4>[below=.4cm of title, align=center] {
        \includegraphics[scale=.7]{posterior_freestreaming}\\[2ex]
        \small Analysis cannot tolerate free-streaming\\
        \small times larger than ${\sim} 1$~fm/$c$
      };
    \node<5>[xshift=-.5cm, yshift=.9cm, scale=.3] {\includegraphics[scale=.15]{magnifying-glass}};
    \node<5>[below=.4cm of title, align=center] {
        \includegraphics[scale=.7]{posterior_structure}\\[2ex]
        \small Parton structure param.\ $\chi_\mathrm{struct} = 0.28_{-0.16}^{+0.17}$,\\
        \small Was used to reparametrize parton width as\\[.5ex]
        \small $v = v_\text{min} + \chi_\text{struct}(w - v_\text{min})$.\\[1ex]
        \small \hfill Let's revert $\chi_\text{struct}$ back to a width...
      };
  \end{tikzpicture}
\end{frame}

\begin{frame}{\scshape Nucleon size and shape}
  \begin{columns}
    \begin{column}{.45\textwidth}
      \begin{figure}
        \includegraphics[width=\textwidth]{proton_posterior_shape}
      \end{figure}
    \end{column}
    \begin{column}{.55\textwidth}
      \begin{itemize}
        \item Parton sampling radius\, $w = 1.04_{-0.15}^{+0.16}$~fm\\[.5ex]
          $^*$Note: the actual rms radius in the center of mass frame is somewhat smaller.\\[2ex]
        \item Parton width\, $v = 0.51_{-0.17}^{+0.19}$~fm\\[.5ex]
          (width of Gaussian constituents)\\[2ex]
        \item Results likely sensitive to model details,
          e.g.\ equation of state, pre-equilibirum dynamics and viscous
          corrections $\delta f$\\[2ex]
      \end{itemize}
    \end{column}
  \end{columns}
\end{frame}

\begin{frame}{\scshape QGP medium properties}
\end{frame}

\begin{frame}{\scshape Maximum a posteriori parameters}
  \begin{center}
    \Large To do if time allows...
  \end{center}
\end{frame}

\appendix

\begin{frame}[plain, noframenumbering]
  \begin{center}
    \Large \scshape Backup slides
  \end{center}
\end{frame}

\begin{frame}{\scshape Emulator validation}
  \begin{columns}
    \begin{column}{.35\textwidth}
      {\scshape Preprocessing}
      \begin{enumerate}
        \item log transform data
        \item subtract mean and divide out variance
        \item project onto principle component basis
      \end{enumerate}
      \medskip
      {\scshape k-fold cross validation}
      \begin{itemize}
        \item Subdivide design into $k$ partitions. Choose one for
          validation and use the rest for training. Repeat for all partitions.
      \end{itemize}
    \end{column}
    \begin{column}{.65\textwidth}
      \includegraphics[width=\textwidth]{validation_example}
    \end{column}
  \end{columns}
\end{frame}

\begin{frame}{\scshape Emulator validation}
    \includegraphics<1>[width=\textwidth]{validation_pPb5020}
    \includegraphics<2>[width=\textwidth]{validation_PbPb5020}
    \begin{itemize}
      \item Model-data residuals should have zero mean and unit variance.
      \item Root-mean square error expressed as percentage of overall design variance.
    \end{itemize}
\end{frame}
